# Extra Discovery Search Exploration

```{r}
# load outputs

docs_searched <- readRDS(file = "./data/docs_searched.RDS")
docs_strings <- readRDS(file = "./data/docs_strings.RDS")
```

# Initial first sentence search
```{r}

dsrch_data <- data.frame(matrix(data = NA, nrow = 1, ncol = 4), stringsAsFactors = FALSE)[-1,]
names(dsrch_data) <- c("doc", "path", "search", "url")

for (i in docs_searched) {
  doc <- i$doc
  path <- i$path
  search <- i$search
  url <- i$url
  row <- cbind(doc, path, search, url)
  dsrch_data <- rbind(dsrch_data, row, stringsAsFactors = FALSE)
}

dsrch_data$url[1:5]
```

The document set is a collection of whole or parts of blog entries from eight2late with some inconsistency. Manual checking and cleaning of these entries to complete the url set. This process would quite challening, impossible or merely a waste of time on corpus that is much larger, and require automation.

```{r}
# very different results from eight to late

# Doc 20
# https://www.pinterest.com.au/pin/423268064964550659/
# searching term and selecting the more appropriate result
# https://eight2late.wordpress.com/2015/07/22/a-gentle-introduction-to-cluster-analysis-using-r/
# replace entry in df

dsrch_data$url[20] <- "https://eight2late.wordpress.com/2015/07/22/a-gentle-introduction-to-cluster-analysis-using-r/"

# Doc 42
# https://www.datacamp.com/community/news/an-intuitive-introduction-to-support-vector-machines-using-r-part-1-wbzf8z3i4p
# https://eight2late.wordpress.com/2018/06/06/an-intuitive-introduction-to-support-vector-machines-using-r-part-1/

dsrch_data$url[42] <- "https://eight2late.wordpress.com/2018/06/06/an-intuitive-introduction-to-support-vector-machines-using-r-part-1/"

# urls that reference a collection of blog entries by month

# Doc 1
dsrch_data$url[1] <- "https://eight2late.wordpress.com/2018/02/05/risk-management-and-organizational-anxiety/"

# Doc 4
dsrch_data$url[4] <- "https://eight2late.wordpress.com/2011/01/20/elephants-in-the-room-seven-reasons-why-project-risks-are-ignored/"

# Doc 7
dsrch_data$url[7] <- "https://eight2late.wordpress.com/2010/06/02/operational-and-strategic-risks-on-projects/"

# Doc 8
dsrch_data$url[8] <- "https://eight2late.wordpress.com/2010/02/11/the-failure-of-risk-management-a-book-review/"

# Doc 15
dsrch_data$url[15] <- "https://eight2late.wordpress.com/2009/04/15/capturing-project-knowledge-using-issue-maps/"

# Doc 17
dsrch_data$url[17] <- "https://eight2late.wordpress.com/2009/06/25/visualising-arguments-using-issue-maps-an-example-and-some-general-comments/"

# Doc 26
dsrch_data$url[26] <- "https://eight2late.wordpress.com/2013/05/07/a-stupidity-based-theory-of-organisations-a-paper-review/"

# Doc 28
dsrch_data$url[28] <- "https://eight2late.wordpress.com/2008/02/26/the-effect-of-organizational-culture-on-project-success/"

# Doc 32
dsrch_data$url[32] <- "https://eight2late.wordpress.com/2010/05/20/on-the-relationship-between-projects-and-organisations/"

# urls that reference a collection by tag or category

# Doc 11
dsrch_data$url[11] <- "https://eight2late.wordpress.com/2014/11/24/from-information-to-knowledge-the-what-and-whence-of-issue-based-information-systems/"

# Doc 18
dsrch_data$url[18] <- "https://eight2late.wordpress.com/2017/02/23/a-prelude-to-machine-learning/"

# Doc 22
dsrch_data$url[22] <- "https://eight2late.wordpress.com/2015/12/02/a-gentle-introduction-to-network-graphs-using-r-and-gephi/"

# Doc 23
dsrch_data$url[23] <- "https://eight2late.wordpress.com/2015/04/07/from-the-coalface-an-essay-on-the-early-history-of-sociotechnical-systems/"


# url not referencing specific articles

# Doc 5
dsrch_data$url[5] <- "https://eight2late.wordpress.com/2011/01/06/there's-trouble-ahead-early-warning-signs-of-project-failure/"

# Doc 16
dsrch_data$url[16] <- "https://eight2late.wordpress.com/2009/04/07/issues-ideas-and-arguments-a-communication-centric-approach-to-tackling-project-complexity/"

# Doc 37
dsrch_data$url[37] <- "https://eight2late.wordpress.com/2011/02/25/the-drunkard's-dartboard-an-intuitive-explanation-of-monte-carlo-methods/"

```

Now each document is linked to a specific artile, these article links conveniently have data and title of the post in a consistent format.

```{r}
dsrch_data$date <- NA
dsrch_data$title <- NA

for (i in 1:nrow(dsrch_data)) {
  ur <- dsrch_data[i,4]
  str <- strsplit(ur, "[/]")
  dte <- paste(str[[1]][4],str[[1]][5],str[[1]][6], sep = "-")
  ttl <- str[[1]][7] 
  dsrch_data[i,5] <- dte
  dsrch_data[i,6] <- ttl
}

titles <- unique(dsrch_data$title)
# all unique articles

dsrch_data$date <- as.Date(dsrch_data$date)
range(dsrch_data$date)
#2008-02-26 to 2018-06-06

dsrch_data$timesincefirst <- floor(difftime(dsrch_data$date, "2008-02-26", units = "days"))

ggplot(dsrch_data, aes(x = date, y = 1)) + geom_point()

head(dsrch_data)

```

## rename docs
```{r, eval=FALSE}
dsrch_data$newpath <- paste("./titleddocs/", dsrch_data$date, "_", dsrch_data$title, sep = "")
file.copy(dsrch_data$path, dsrch_data$newpath, copy.mode = TRUE, copy.date = TRUE)
```




## check matching?

```{r}
init_clus <- readRDS(file = "./data/initial_clusters.RDS")
lsa_clus <- readRDS(file = "./data/lsa_clusters.RDS")
lda_clus <- readRDS(file = "./data/lda_group.RDS")

cluster_output <- merge(init_clus, lsa_clus, by = "rowname")
cluster_output <- merge(cluster_output, lda_clus, by = "rowname")
```

lda and lsa are relaitlvly consistent

## Themes over time

group by time
```{r}
cluster_output$date <- dsrch_data$date

ggplot(cluster_output, aes(x = date, y = lda4topic)) + geom_point()
```
topic groupings do not appear to be conistent with distribution over time

```{r}
cluo <- cluster_output %>% 
  select(-rowname)
cluo$date <- as.numeric(cluo$date)
pairs(cluo)

shared <- proxy::dist(cluo, method = NMI, pairwise = TRUE, by_rows = FALSE)
shared <- as.matrix(shared)
corrplot(shared, method = "number")

```

